Proposed Solution

### 2016-01-29 intro1.tex
random

From a  practical perspective there is no additional burden 
to the users: they can simply use \app to check for errors in their configuration files. However, they can also easily extend the framework themselves. The system is designed to be highly modular. If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class. The new learner can be added to \app and this way it can check additionally a new set 
for even more errors.

>>>>

From a  practical perspective there is no additional burden 
to the users: they can simply use \app to check for errors in their configuration files. However, they can also easily extend the framework themselves. The system is designed to be highly modular. If there is a class of rules that \app is not currently learning, the user can develop their own templates and learners for that class. The new learner can be added to \app and this way it can check additionally a new set of errors.

Finally, from a system perspective this is the first approach that checks

\xxx{I think we should explicitly 
mention our approach aims to solve 
misconfiguration from different way with the
previous work. Previous work tries to find out the problem after the
failures occur, but our approach is a proactive method, which can
find out error before the system failure occurs. Such an effort (i.e., 
preventing misconfiguration before installation) is
important, because the majority of errors can be 
detected before running your system. 
Thus, 1) users will not complain too much because they are using
``very healthy'' configuration files, 
and 2) this is a great complementary to existing reactive misconfiguration 
detectors. -- Ennan}
